---
title: "HCG trigger of GnRH agonist-induced functional ovarian cysts does not decrease clinical pregnancy rate in GnRHa pretreated frozen cycles: evidence from a retrospective cohort study"
author:
  - Hong Zeng 
documentclass: ctexart
keywords:
  - Gonadotrophin releasing hormone agonist
  - Functional ovarian cyst
  - hCG trigger
  - Frozen-thawed embryo transfer
  - Hormone replacement therapy
geometry: "left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.2cm"
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 5
---
# first load the data
```{r}
load("Data.Rda")#load data
df[unique(df$ID), ]%>% nrow()#count the number of patients
nrow(df)#count the number of FET cycles
```

# Table 1
## Charateristics description of the crude cohort
```{r Table 1 charateristics, echo=TRUE, message=FALSE, warning=FALSE}
if(!"compareGroups" %in% installed.packages()){
  install.packages('compareGroups')}
library(compareGroups)
table1 <- descrTable(group ~ Age + Infertility_cause + Endometrial_thick + BMI + bFSH + Endometrial_pattern, data=df, show.all=T,  method = c( bFSH=2), p.corrected = F, digits = 2)
table1
```

## calculate the cancel rate of Table 1
```{r Table 1 cancer rate, echo=TRUE, message=FALSE, warning=FALSE}
if(!"tidyverse" %in% installed.packages()){
  install.packages('tidyverse')}
library(tidyverse)
cancel_rate <- df %>% group_by(group) %>% count(No_ET) %>% filter(No_ET=="0")
cancel_rate
options(digits = 6)
chisq.test(matrix(data=c(14, 579, 5, 59), nrow = 2, byrow = T), correct = F)
```

# Table 2 
## Multivariate regression analysis revealed the risk factors associated with the incidence of FC
### age and BMI as continous vairables (model1)
```{r Table 2 model1, echo=TRUE, message=FALSE, warning=FALSE}
if(!"tidyverse" %in% installed.packages()){
  install.packages('tidyverse')}
if(!"geepack" %in% installed.packages()){
  install.packages('geepack')}
if(!"gtsummary" %in% installed.packages()){
  install.packages('gtsummary')}
library(tidyverse)
library(geepack)
library(gtsummary)
df <- within(df, {
  group_num <- NA
  group_num[group == "Control group"] <- 0
  group_num[group == "Follicle group"] <- 1
})
tbl_gee_FC1 <- geeglm(group_num ~ Age + BMI, id = ID, data = df, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_FC1
```

### age and BMI as categorical vairables (model2)
```{r Table 2 model2, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(geepack)
library(gtsummary)
tbl_gee_FC2 <- geeglm(group_num ~ Cat_Age + Cat_BMI, id = ID, data = df, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_FC2
```

# Table 3
## Statistical description of the included cohort after excluding the cycles with exclusion criteria before PSM
```{r Table 3 Baseline characteristics and pregnancy outcomes before PSM, echo=TRUE, message=FALSE, warning=FALSE}
table2 <- descrTable(group ~ Age + Infertility_cause + Endometrial_thick + Endometrial_pattern + BMI + bFSH + Embryo_type + No_ET + No_GEm + CP + Miscarriage + EP, data=df_select, show.all=F,  method = c( bFSH=2), p.corrected = F, digits = 2)
table2
```

## Calculate the implantation rate before PSM
```{r Table 3 implantation rate before PSM, echo=TRUE, message=FALSE, warning=FALSE}
# 胚胎着床率
library(tidyverse)
IMR_beforePSM <- df_select %>% group_by(group) %>% summarise(total_sac=sum(No_sacs), total_ET=sum(No_ET_num), IMR=sum(No_sacs)/sum(No_ET_num)) 
IMR_beforePSM
options(digits = 6)
chisq.test(as.matrix(IMR_beforePSM[,c("total_sac", "total_ET")]), correct = F)
```

## propensity score mathcing(PSM)-1:1matching
```{r PSM, echo=TRUE, message=FALSE, warning=FALSE}
if(!"MatchIt" %in% installed.packages()){
  install.packages('MatchIt')}
library(MatchIt)
set.seed(12345678)
matched_data1 <- MatchIt::matchit(group~Age + BMI + No_ET + No_GEm + Embryo_type, data=df_select, method = "nearest", ratio=1, caliper=0.02)
summary(matched_data1)
data_matched1 <- MatchIt::match.data(matched_data1)
plot(matched_data1, type = "jitter")
plot(matched_data1, type = "hist")
```

## Statistical description of the included cohort after excluding the cycles with exclusion criteria after PSM
```{r Table 3 Baseline characteristics and pregnancy outcomes after PSM, echo=TRUE, message=FALSE, warning=FALSE}
if(!"compareGroups" %in% installed.packages()){
  install.packages('compareGroups')}
library(compareGroups)
table_match1 <- descrTable(group ~  Age + Infertility_cause + Endometrial_thick + Endometrial_pattern + BMI + bFSH + Embryo_type + No_ET + No_GEm + CP + Miscarriage + EP, data=data_matched1, show.all=F,  method = c( bFSH=2), p.corrected = F, digits = 2)
table_match1
```

## Calculate the implantation rate after PSM
```{r Table 3 implantation rate after PSM, echo=TRUE, message=FALSE, warning=FALSE}
if(!"tidyverse" %in% installed.packages()){
  install.packages('tidyverse')}
library(tidyverse)
IMR_afterPSM <- data_matched1 %>% group_by(group) %>% summarise(total_sac=sum(No_sacs), total_ET=sum(No_ET_num), IMR=sum(No_sacs)/sum(No_ET_num)) 
IMR_afterPSM
options(digits = 6)
chisq.test(as.matrix(IMR_afterPSM[,c("total_sac", "total_ET")]), correct = F)
```

# Table 4
## Multivariate regression analysis revealed the effect of HCG triggering GnRHa-induced FC on clinical pregnancy
### Model1--adjusted for the number of transferred embryos, the number of transferred good-quality embryos, and the type of transferred embryos
```{r Table 4 model1, echo=TRUE, message=FALSE, warning=FALSE}
if(!"tidyverse" %in% installed.packages()){
  install.packages('tidyverse')}
if(!"geepack" %in% installed.packages()){
  install.packages('geepack')}
if(!"gtsummary" %in% installed.packages()){
  install.packages('gtsummary')}
library(tidyverse)
library(geepack)
library(gtsummary)
tbl_gee_CP1 <- geeglm(CP_num ~ group + No_ET + No_GEm + Embryo_type, id = ID, data = df_select, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP1
```

### model2--adjusted for the number of transferred embryos, the number of transferred good-quality embryos, the type of transferred embryos, female age, and BMI
```{r Table 4 model2, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(geepack)
library(gtsummary)
tbl_gee_CP2 <- geeglm(CP_num ~ group + Cat_Age + Cat_BMI + No_ET + No_GEm + Embryo_type, id = ID, data = df_select, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP2
```

### model3-adjusted with the number of transferred embryos, the number of transferred good-quality embryos, the type of transferred embryos, female age, BMI, endometrial thickness, and endometrial pattern,
```{r Table 4 model3, echo=TRUE, message=FALSE, warning=FALSE}
library(geepack)
library(gtsummary)
library(tidyverse)
tbl_gee_CP3 <- geeglm(CP_num ~ group + Cat_Age + Cat_BMI + No_ET + No_GEm + Embryo_type + Cat_EndoThickofET + Endometrial_pattern, id = ID, data = df_select, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP3
```

# The interactive analysis
```{r interactive analysis, echo=TRUE, message=FALSE, warning=FALSE}
if(!"tidyverse" %in% installed.packages()){
  install.packages('tidyverse')}
if(!"geepack" %in% installed.packages()){
  install.packages('geepack')}
if(!"gtsummary" %in% installed.packages()){
  install.packages('gtsummary')}
library(tidyverse)
library(geepack)
library(gtsummary)
gee_interactive <- geeglm(CP_num ~ group + Cat_Age + Cat_BMI + No_ET + No_GEm + Embryo_type + Cat_Age:group, data = df_select,family = binomial(logit), id = ID, corstr="independence")
summary(gee_interactive)
fit_interactive <- glm(CP ~ group + Cat_Age + Cat_BMI + No_ET + No_GEm + Embryo_type + Cat_Age:group, data = df_select,family = binomial(logit))
summary(fit_interactive)
fit_non_interactive <- glm(CP ~ group + Cat_Age + Cat_BMI + No_ET + No_GEm + Embryo_type, data = df_select,family = binomial(logit))
summary(fit_non_interactive)
if(!"lmtest" %in% installed.packages()){
  install.packages('lmtest')}
library(lmtest)
lrtest(fit_interactive, fit_non_interactive)
```

# Table 5
## Subgroup analysis based on age
### age >= 35 subgroup
```{r Table 5 age > 35 subgroup, echo=TRUE, message=FALSE, warning=FALSE}
df_select_35 <- subset(df_select, Age>="35")
table(df_select_35$group)
tbl_gee_CP_35 <- geeglm(CP_num ~ group + Cat_BMI + No_ET + No_GEm + Embryo_type, id = ID, data = df_select_35, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP_35
```

### age < 35 subgroup
```{r Table 5 age < 35 subgroup, echo=TRUE, message=FALSE, warning=FALSE}
df_select_35s <- subset(df_select, Age<"35")
table(df_select_35s$group)
tbl_gee_CP_35s <- geeglm(CP_num ~ group + Cat_BMI + No_ET + No_GEm + Embryo_type, id = ID, data = df_select_35s, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP_35s
```

## Subgroup analysis based on embryo type
### cleavage embryo subgroup
```{r}
df_select_cleavage <- subset(df_select, Embryo_type == "cleavage")
table(df_select_cleavage$group)
tbl_gee_CP_cleavage <- geeglm(CP_num ~ group + Cat_BMI + No_ET + No_GEm, id = ID, data = df_select_cleavage, corstr="independence", family = binomial(logit)) %>% tbl_regression(exponentiate = TRUE)
tbl_gee_CP_cleavage
```

## blastocyst embryo subgroup
```{r}
df_select_blastocyst <- subset(df_select, Embryo_type == "blastocyst")
table(df_select_blastocyst$group)
```


